Automated Topic Naming

### 2012-01-18 ese/ese.tex
I hope this isn't some phantom commit where I wrecked something

Empirically how poor were our results? We decided to compare our
results against simulated or random results. In the first simulation
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling versus our labelling, and repeated
this 10000 times, we found that
for 4 out of 7 NFR labels, our labels IRR were greater than the random
IRR measures 95\% of the time. For portability and efficiency, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. Figure \ref{fig:irr} depicts the IRR of
these sampled ratings versus our IRR using the Kappa statistic.

@@

>>>>

Empirically how poor were our results? We decided to compare our
results against simulated or random results. In the first simulation
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling versus our labelling, and repeated
this 100,000 times, we found that
for 4 out of 7 NFR labels, our labels IRR were greater than the random
IRR measures 96\% of the time. For portability and efficiency, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. Figure \ref{fig:irr} depicts the IRR of
these sampled ratings versus our IRR using the Kappa statistic.

@@

% [1] "Person  Abram"
% [1]  3.093543e-06  1.269107e-04 -5.132487e-05 -1.449561e-05  7.953201e-05
% [6] -2.791593e-05  6.246161e-05
% [1] "Person ECDF measures Abram"
% [1] 0.99992 0.36418 0.55153 0.97717 1.00000 0.64988 0.96132
% [1] "Person  Neil"
% [1] -1.426950e-04 -8.394072e-06 -1.108948e-04  8.568950e-06 -1.531356e-06
% [6]  3.387974e-05 -9.010485e-05
% [1] "Person ECDF measures Neil"
% [1] 0.99994 0.36777 0.55371 0.97775 1.00000 0.59585 0.92487
% [1] "Person  Both"
% [1] -1.026767e-04  2.685101e-05  2.550572e-06  5.996015e-05 -4.787163e-05
% [6] -1.982510e-04 -8.891684e-05
% [1] "Person ECDF measures Both"
% [1] 0.99995 0.37230 0.57847 0.96622 0.99998 0.90559 0.99859
